Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-09-10 journal-draft/ettdoc.tex
minor changes in the related work

In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in the cluster.
In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
As the activity of primary users is usually unknown to the secondary users, it is deemed as random as to secondary users.
Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
In other words, such clusters are more robust.
In this paper, the robustness of a cluster is the ability to sustain with the existence of primary users.
%
Within in a cluster, both payload and control overheads can be transmitted on the CCs.
%Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
When one or several cluster members can not access one certain CC on which primary some user activity is detected, the channel will be excluded from the set of CCs.
In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
%As long as there is a CC available, the corresponding cluster can continue to exchange payload data.

@@

Here we give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
%%[crn for clustering] 
%%due to attenuation of signal propagation, primary users can only be detected by CR users when they locate closely to CR users.
%In cognitive radio networks, secondary users which locate closely with each other are possibly affected by the same group of primary users, so that the availability of licensed spectrum is similar to them, \ie certain channels are available on each of them.
%The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.
%[robustness issue for clustering]
%%%%%%%%%%%
%On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden. 
%Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
%%%%%%%%%%%%
%with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
%that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
%Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
%When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
%%%%%%%%%%%%%
%Various clustering schemes are proposed to target different aspects in cognitive radio networks.
%Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users with potentially best detection performance into the same cluster.
%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
%\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and enforce that every cluster possesses at least one CC.
Clustering scheme~\cite{Consensus_based_clustering12} looks for a network partition which improves the accuracy of spectrum sensing with the cluster structure.
%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
\cite{TWC2012_cooperative_communication} forms the clusters by deciding on the cluster heads, where the transmit power for the long-haul transmission between the cluster heads is minimized.
\cite{clustering_globecom11} proposes a cluster structure which promises energy efficiency.
\cite{cluster_EW10} proposes strategy on how to decide on the CCs and access the multiple CCs within clusters.
An event-driven clustering scheme is proposed for cognitive radio sensor networks in \cite{Ozger_cluster_crsn_13}.
None of the above mentioned schemes provides a certain robustness to formed clusters against primary users.

@@

Furthermore, this work doesn't consider the robustness of clusters against the increasing activity of primary users, which leaves their claim of robustness unverified.

>>>>

In CRN, a formed cluster seizes one or multiple unlicensed channels which are available for every CR node in the cluster.
In this paper available unlicensed channels are called \textit{common licensed channels} (or common channels for short, which is abbreviated as CC).
The availability of CCs within a cluster decides the existence of that cluster, \ie if no CCs are available then the corresponding cluster does not exist.
As the activity of primary users is usually unknown to the secondary users, it is deemed as random as to secondary users.
Consequently, a cluster which secures more CCs will anticipate a longer life expectancy. 
In other words, such clusters are more robust.
In this paper, the robustness of the clusters is their ability to sustain with the existence of primary users.
%
Within in a cluster, both payload and control overheads can be transmitted on the CCs.
%Out of the available CCs, there are always one or multiple channels which are used for the payload communication.
When one or several cluster members can not access one certain CC on which primary some user activity is detected, the channel will be excluded from the set of CCs.
In particular, if that channel is being used for payload communication, the communication pair will stop and resume the transmission on another available CC.
%As long as there is a CC available, the corresponding cluster can continue to exchange payload data.

@@

In the following we will give a brief review on the clustering in CRN, with emphasis on the theme of robust clustering.
%%[crn for clustering] 
%%due to attenuation of signal propagation, primary users can only be detected by CR users when they locate closely to CR users.
%In cognitive radio networks, secondary users which locate closely with each other are possibly affected by the same group of primary users, so that the availability of licensed spectrum is similar to them, \ie certain channels are available on each of them.
%The similarity of available spectrum on a group of neighbouring CR nodes, along with the benefit of collaborative decision among multiple nodes, leads to clustering as an effective approach for many applications.
%[robustness issue for clustering]
%%%%%%%%%%%
%On the other hand, large clusters are not preferred in some scenarios neither, \eg for the CRN composed with resource limited users, managing the cluster members in a large cluster is a substantial burden. 
%Hence, the cluster size should fall in a desired range according to different application scenarios~\cite{Chen04clusteringalgorithms, capacity_cluster_06}.
%%%%%%%%%%%%
%with the intention to provide a robust infrastructure for the applications which may be conducted above that in CRN.
%that being said, when we design this clustering scheme in CRN, we do consider the services to be delivered by the network.
%Cluster sizes affect the power consumption directly in wirelss sensor networks~\cite{clustering_globecom11, EnergyEfficientClusteringRouting_2015}.
%When the cluster size is not deliberately discussed, it is also decided alongside the optimization of the network, \eg the opimal selection of the aggregation points in a wireless sensor network results in the clusters~\cite{data_aggr_algorithm_04}.
%%%%%%%%%%%%%
%Various clustering schemes are proposed to target different aspects in cognitive radio networks.
%Work~\cite{Consensus_based_clustering12} improves spectrum sensing ability by grouping the CR users with potentially best detection performance into the same cluster.
%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
%\cite{clustering_globecom11} proposes clustering strategy in cognitive radio network, which looks into the relationship between cluster size and power consumption and accordingly controlling the cluster size to decrease power consumption.
With regard to forming clusters in CRN, deciding on the common channel within each cluster is the foremost question to answer.
\cite{Zhao07, Chen07,Affinity_clustering_09icccn} propose the clustering schemes and enforce that every cluster possesses at least one CC.
Clustering scheme~\cite{Consensus_based_clustering12} looks for a network partition which improves the accuracy of spectrum sensing with the cluster structure.
%Clustering scheme~\cite{clustering_globecom11} obtains the best cluster size which minimizes power consumption caused by communication within and among clusters.
\cite{TWC2012_cooperative_communication} forms the clusters by deciding on the cluster heads, where the transmit power for the long-haul transmission between the cluster heads is minimized.
\cite{clustering_globecom11} proposes a cluster structure which promises energy efficiency.
\cite{cluster_EW10} proposes strategy on how to decide on the CCs and access the multiple CCs within clusters.
An event-driven clustering scheme is proposed for cognitive radio sensor networks in \cite{Ozger_cluster_crsn_13}.
None of the above mentioned schemes provides a certain robustness to formed clusters against primary users.

@@

Furthermore, both this work and SOC define robustness just to be the number of CCs per cluster, and don't consider the sustainability of clusters against the increasing activity of primary users, which leaves their claim on robustness unverified.
